\textbf{Predicting virus-receptor mutant binding by molecular dynamics simulation}

### 2013-06-20 paper.tex
Some copy editing.

The computational prediction of mutational effects on protein--protein interactions remains a challenging problem. Several methods are available to perform an energy difference calculation from an experimentally determined co-crystal structure. For example, computational alanine-scanning can be performed rapidly, with relatively low computational cost \citep{Grant2011,Kortemme2004}. However, such methods calculate the relative contribution to overall energy for each amino acid in a protein. They do not probe the interface directly, but rather calculate the total energy with each substitution \citep{Grant2011,Kortemme2004}. Alternative approaches have been developed using machine learning, training coefficients in a weighted equation containing geometric and energetic parameters \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. Unfortunately, such machine-learning approaches often suffer in novel applications, for which available training sets are small or non-existent. As such, these methods are poorly suited for most host-virus protein--protein systems. By contrast, first principles methods offer the chance to forgo training. However, the currently available methods such as free energy perturbation (FEP) and thermodynamic integration (TI) rely on a two state model that phases directly from one three dimensional protein model to another with no intermediate transition states \citep{Gilson1997,Lu2004}. Thus, they can quickly lose physiological relevance as the two proteins become more dissimilar and as a result are largely limited to testing only sequential point mutants.

@@

We applied our method to interrogate the interaction between machupo virus (MACV) spike glycoprotein (GP1) and the human transferrin receptor (hTfR1) \citep{Abraham2010,Charrel2003}. Machupo is a negative-sense RNA virus of the arenavirus family \citep{Charrel2003}. Worldwide arenaviruses represent a significant source of emerging zoonotic diseases for the human population \citep{Charrel2003}. Members of the arenavirus family include the lassa fever virus endemic to West Africa, the lymphochoriomeningitis virus (LCMV) endemic to rodents in several areas of the United States, and the guanarito, junin and machupo viruses endemic to rodents in South America \citep{Charrel2003}. The South American arenaviruses typically infect humans after rodent contamination and cause a devastating hemorrhagic fever with very high mortality \citep{Charrel2003}.

@@

We applied our method to wild type (WT) and mutant complexes, and found that we could resolve relative differences in unbinding and predict significant affinity changes. At sites known to be important for successful viral entry, we found that the biochemical cause of reduced infectivity is often not as simple as the static structure suggests. For example, the static structure shows a hydrogen-bonding network connected to site Asn348 in hTfR1. According to our simulations, this network likely does not affect binding affinity. Our study offers an all-atom steered molecular dynamic approach to avoid the pitfalls of several existing methods used to evaluate mutations in host-virus protein--protein interfaces.

@@

In every way possible the subsequent steering simulation had the same parameters as the equilibration simulation. Thus, the steered molecular dynamics (SMD) \citep{Is2001B} simulation was a typical restart with slightly different settings. Periodic boundary conditions were incorporated as part of the system and PME was again used to approximate full system electrostatics. In addition, we first tuned the pulling velocity for practical time considerations. Subsequently, the spring constant was adjusted to ensure sufficient signal to noise with the given velocity. As a result, the spring constant was set to 5 (units), velocity set to 2 (units), and direction down the positive $z$-axis.

Finally, SMD was run for 15 ns (7,500,000 time steps) of chemical time. For each simulation, we randomly selected one of the equilibration runs for restart. We ran 50 replicate simulations per mutant. All GP1/hTfR1 complexes separated by greater than 4 \AA ngstroms and many separated to 10 or more.

@@

\subsection*{Steered molecular dynamics simulations}
To ensure a natural solution structure, we performed an initial equilibration phase to reduce the intrinsic crystallization distortions. First, we generated a physically realistic simulation world around the protein complex. The environment included an explicitly modeled bath of water, and a physiologically relevant concentration of ions. Next, with a fixed $\alpha$-carbon backbone we carried out successive rounds of energy minimization, followed by heating, and backbone release. Last,  with minimal restraints a short round of all-atom molecular dynamics \citep{Cuendet2008} was performed. We used the final state from each equilibrated system to restart another MD simulation. For SMD, at the centroid of several atoms a force was applied to a single point in GP1. By using a known spring constant, and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. The force curves for each mutant were smoothed either by averaging over many replicates as in Figure~\ref{fig:force_curve} or by selecting an interpolation window for averaging. The latter approach was used for statistical analysis. In addition, to minimize the computational time in unproductive molecular dynamics, we shortened the simulation time such that the interaction just barely dropped to zero near the end of each run. As seen in Figure~\ref{fig:force_curve}, this distance was relatively consistent among mutants. The supplementary movie visually illustrates the separation distance between peptide domains. The quantities MAF and AUC were derived from the force versus distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_statistics}). The largest single-mutant impact was seen for a mutation to alanine at site Tyr211 in the hTfR1 ($ p < 0.001 $).  Several mutations at this site have proven capable of causing loss-of-infection, according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure \citep{Abraham2010}. In agreement with the static structure, our molecular dynamics simulations show Tyr211 is involved in a large hydrogen-bonding network (results not shown).

@@

We also simulated several point mutations at Asn348 in the hTfR1. Asn348Lys is reported in the literature to cause reduced infectivity \textit{in vivo} \citep{Rad2008,Abraham2010}. Further, in the crystal structure two residues on GP1 and at least three on hTfR1 are involved in a fairly extensive hydrogen-bonding network. As discussed above, the alanine mutation at this site showed no significant difference in MAF or AUC from WT (Tables~\ref{tab:MAF_p} and ~\ref{tab:AUC_p}). In addition, the Asn348Lys mutation showed no significant difference from WT, and neither did Asn348Trp. (For both of these mutations, mean MAF and mean AUC was lower than for WT, however. See Table~\ref{tab:summary_statistics})  On the other hand, there was a detectable difference between Asn348Ala and Asn348Lys (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), with Asn348Lys being a weaker binder. Moreover, Asn348Trp showed nearly identical results to Asn348Lys. These results suggest that, in contrast to Tyr211, the critical difference at position 348 in hTfR1 is size exclusion rather than the destruction of a hydrogen-bonding network. The mutations to large amino acids (Asn348Trp and Asn348Lys) produced nearly identical affinity changes, whereas the mutations to amino acids not capable of hydrogen bonding (Asn348Ala and Asn348Trp) produced significantly different affinity changes (Table~\ref{tab:pairwise_differences}). To check the consistency of our results, we hypothesized that the combination of Tyr211Ala and Asn348Trp, being chemically disconnected in two different hydrogen-bonding networks, would lead to a synergistic loss-of-binding. As expected, the double mutant was the weakest binding mutant tested ($ p < 10^{-6} $) (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}) in this study. Further, according to MAF (but not AUC), the combination of Tyr211Ala and Asn348Trp also showed significantly weaker binding than Tyr211Ala by itself (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}). We suspect that the effect of Asn348Trp alone is near the limit of detection using our method. A larger number of replicates would possibly have resolved affinity differences between Asn348Trp and WT or other mutants more consistently.

@@

By extending the SMD technique to investigate a protein--protein interaction we have, in many ways, changed the scope of its application. Traditionally this technique is either applied to compute equilibrium quantities via a non-equilibrium approximation \citep{Park2003,Park2004,Buch2011,Giorgino2012}, used to estimate protein stability through unfolding \citep{Lu1999}, or used to calculate the absolute free energy of small molecule ligand binding \citep{Dixit2001}. Likewise, others have used SMD to understand the process of binding and unbinding at a resolution unmatched by experiment \citep{Cuendet2011,Giorgino2012}. And still others aimed at more esoteric problems apply driving forces to untie polypeptide knots in toy systems \citep{Sulkowska2010}. Here, we have shown that SMD can provide some insight into the \textit{relative} strength of protein--protein interactions. In contrast to more traditional absolute affinity calculations, relative binding is much more useful for experimental application. Further, our method complements whole cell infectivity assays, which demonstrate phenotypic effects but do not provide biochemical mechanisms. Via SMD, one can separate mutations whose likely effect is altered binding affinity from mutations that may affect other factors such as protein expression, protein folding, or interactions with other proteins not considered in the simulation. Thus, SMD may open avenues for subsequent experimental work.

Our findings rationalize several effects observed in both infectivity data and rodent populations \citep{Rad2008,Rad20111}. We found that some substitutions at positions 211 and 348 did negatively affect the strength of viral binding. In the two cases, the computational data suggests that the reason and nature of the effects are very different. Congruent with infectivity data, mutations at Tyr211 often have a dramatic effect on receptor binding \citep{Rad2008,Rad20111}. Tyr211Ala alone produces such a large decrease in affinity that it can be easily distinguished from the WT complex. Structural analysis reveals that the biochemical cause involves the destruction of a critical hydrogen-bonding network with Ser113 and vArg111 in GP1. Further, Tyr211Asp and Tyr211Thr were easily resolved from the WT complex, but they appear to cause an increase in affinity. As a result, we predict experimental structural analysis will show Tyr211Asp and Tyr211Thr mutations cause a relatively dramatic tertiary structure deviation. Given that our model starts from an associated complex, it is not surprising that Tyr211Asp would cause increased rather than decreased affinity. Aspartate is charged rather than polar at physiological pH and its shorter side chain means the proteins would be pulled in closer apposition. Nevertheless, our results show Tyr211, or some other amino acid that is capable of hydrogen bonding, is necessary for a stable hydrogen-bonding network leading to efficient binding. Moreover, the cause of decreased infectivity seen in rodent populations with the Tyr211Asp mutation is not a simple change in binding affinity.

@@

Although our computational predictions largely agreed with the available literature, some mutations that are reported to cause reduced infectivity in experimental systems (most notably vArg111Ala and Asn348Lys, discussed above) were indistinguishable from the WT complex in our simulations. We would like to emphasize here that we cannot expect perfect agreement. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. It is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). In addition, the available experimental data for the GP1/hTfR1 system were generally obtained from infection assays, not binding assays. There are several reasons other than binding due to which a viral mutation may cause a phenotypic difference in infectivity. First, from infectivity experiments it is not clear the extent to which a protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique may further clarify large-scale folding differences. Second, since we start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) would be underestimated by our method. Third, it is tempting to think only decreased binding affinity should correlate strongly with diminished infectivity. However, dramatically increased binding affinity would also disrupt infectivity by prohibiting cellular membrane detachment after viral invasion. The virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.

@@

Making accurate predictions regarding the effects of non-alanine mutations at protein--protein interfaces remains  challenging. The main obstacle is the enormous number of chemically allowed three dimensional configurations in proteins \citep{Gumbart2012}. In theory, one could carry out all-atom simulations from physical first principles \citep{Gumbart2012} for very long time periods. After equilibrium is reached in such simulations, one could then compute a binding constant by observing the fractional association/dissociation time among two proteins. Unfortunately, due to limited computational power and available methods, reaching equilibrium with a simulated protein system is truly a herculean task and is essentially impossible at this time \citep{Gumbart2012}. There are two broadly useful computational approaches that avoid first-principles equilibrium simulations. First, to reduce computational complexity several studies have used rigid body docking and machine learning \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. While these approaches can work well in certain scenarios, they often underperform in applications to novel systems, due to their dependence on available training data. Second, hybrid approaches exist that exploit non-equilibrium calculations within the context of all atom simulations \citep{Dixit2001,Is2001A,Is2001B,Park2004,Grant2011,Kortemme2004,Gumbart2012}. However, to date most of these methods have not been applied to protein--protein interactions (but rather to simpler scenarios such as protein--ligand interactions). What we have shown here is that hybrid non-equilibrium approaches can provide a useful and practical tool in studying protein--protein interactions.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/protein_comparison.pdf}}
\caption{\label{fig:protein_comparison}\title{Comparison of GP1/hTfR1 complex.} Figure A shows the full, de-glycosylated GP1/hTfR1 co-crystal structure. For figure B, we show the reduced structure for SMD. GP1 is blue and hTfR1 is green.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/force_curve.pdf}}
\caption{\label{fig:force_curve}\title{Force versus distance curve of Y211A mutant and WT.} The average force curve for 50 replicates of the WT complex was black, and the average of 50 replicates of the Y211A mutant was red. Notice there is a very large difference in MAF and AUC between the two complexes.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/sensitivity_histogram.pdf}}
\caption{\label{fig:sensitivity}\title{Density plot of three different GP1/hTfR1 complexes.} The WT GP1-hTfR1 complex in the middle is flanked by the tighter binding mutant Y211D on the right and the weaker binding double mutant N348W/Y211A on the left. The large non-overlapping areas indicate a large and statistically significant difference in these three complexes with relatively minor differences.}
\end{figure}

>>>>

The computational prediction of mutational effects on protein--protein interactions remains a challenging problem. Several methods are available to perform an energy difference calculation from an experimentally determined co-crystal structure. For example, computational alanine-scanning can be performed rapidly, with relatively low computational cost \citep{Grant2011,Kortemme2004}. However, such methods calculate the relative contribution to overall energy for each amino acid in a protein. They do not probe the interface directly, but rather calculate the total energy with each substitution \citep{Grant2011,Kortemme2004}. Alternative approaches have been developed using machine learning, training coefficients in a weighted equation containing geometric and energetic parameters \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. Unfortunately, such machine-learning approaches often suffer in novel applications, for which available training sets are small or non-existent. As such, these methods are poorly suited for most host-virus protein--protein systems. By contrast, first principles methods offer the chance to forgo training. However, the currently available methods such as free energy perturbation (FEP) and thermodynamic integration (TI) rely on a two state model that phases directly from one three-dimensional protein model to another with no intermediate transition states \citep{Gilson1997,Lu2004}. Thus, they can quickly lose physiological relevance as the two proteins become more dissimilar and as a result are largely limited to testing only sequential point mutants.

@@

We applied our method to interrogate the interaction between machupo virus (MACV) spike glycoprotein (GP1) and the human transferrin receptor (hTfR1) \citep{Abraham2010,Charrel2003}. Machupo is a negative-sense RNA virus of the arenavirus family \citep{Charrel2003}. Worldwide, arenaviruses represent a significant source of emerging zoonotic diseases for the human population \citep{Charrel2003}. Members of the arenavirus family include the lassa fever virus endemic to West Africa, the lymphochoriomeningitis virus (LCMV) endemic to rodents in several areas of the United States, and the guanarito, junin, and machupo viruses endemic to rodents in South America \citep{Charrel2003}. The South American arenaviruses typically infect humans after rodent contamination and cause a devastating hemorrhagic fever with very high mortality \citep{Charrel2003}.

@@

We applied our computational method to wild type (WT) and mutant complexes, and found that we could resolve relative differences in unbinding and predict significant affinity changes. At sites known to be important for successful viral entry, we found that the biochemical cause of reduced infectivity is often not as simple as the static structure suggests. For example, the static structure shows a hydrogen-bonding network connected to site Asn348 in hTfR1. According to our simulations, this network likely does not affect binding affinity. Our study offers an all-atom steered molecular dynamic approach to avoid the pitfalls of several existing methods used to evaluate mutations in host-virus protein--protein interfaces.

@@

In every way possible the subsequent steering simulation had the same parameters as the equilibration simulation. Thus, the steered molecular dynamics (SMD) \citep{Is2001B} simulation was a typical restart with slightly different settings. Periodic boundary conditions were incorporated as part of the system and PME was again used to approximate full system electrostatics. In addition, we first tuned the pulling velocity for practical time considerations. Subsequently, the spring constant was adjusted to ensure a sufficient signal-to-noise ratio with the given velocity. As a result, the spring constant was set to 5~kcal/mol/\AA$^2$, velocity set to 1~\AA/ns, and direction down the positive $z$-axis.

Finally, SMD was run for 15 ns (7,500,000 time steps) of chemical time. For each simulation, we randomly selected one of the equilibration runs for restart. We ran 50 replicate simulations per mutant. All GP1/hTfR1 complexes separated by greater than 4 \AA\ and many separated to 10 or more.

@@

\subsection*{Steered molecular dynamics simulations}
To ensure a natural solution structure, we performed an initial equilibration phase to reduce the intrinsic crystallization distortions. First, we generated a physically realistic simulation world around the protein complex. The environment included an explicitly modeled bath of water, and a physiologically relevant concentration of ions. Next, we carried out successive rounds of energy minimization with a fixed $\alpha$-carbon backbone, followed by heating, and backbone release. Last, we performed a short round of all-atom molecular dynamics with minimal restraints \citep{Cuendet2008}. We used the final state from each equilibrated system to restart another MD simulation. For SMD, at the centroid of several atoms a force was applied to a single point in GP1. By using a known spring constant, and pulling with a constant velocity, we could calculate the applied force during protein--protein dissociation \citep{Cuendet2008,Cuendet2011}. A typical averaged force curve comparison can be seen in Figure~\ref{fig:force_curve}. The force curves for each mutant were smoothed either by averaging over many replicates as in Figure~\ref{fig:force_curve} or by selecting an interpolation window for averaging. The latter approach was used for statistical analysis. In addition, to minimize the computational time in unproductive molecular dynamics, we shortened the simulation time such that the interaction just barely dropped to zero near the end of each run. As seen in Figure~\ref{fig:force_curve}, this distance was relatively consistent among mutants. The supplementary movie visually illustrates the separation distance between peptide domains. The quantities MAF and AUC were derived from the force versus distances curves. Their summary statistics are reported in Table~\ref{tab:summary_statistics}. As we are more interested in the phenotypic impact of interface mutations we avoided many of the more physically rigorous, but technically complicated calculations that are possible with SMD \citep{Is2001A,Is2001B}.

@@

In total, we tested 7 point mutants and 3 double mutants in addition to the WT complex (Table~\ref{tab:summary_statistics}). The largest single-mutant impact was seen for a mutation to alanine at site Tyr211 in the hTfR1 ($ p < 0.001 $).  Several mutations at this site have proven capable of causing loss-of-infection, according to \textit{in vitro} flow-cytometry infection assays or known host-range limitations \citep{Rad2008,Rad20111,Rad20112}. Most likely, this effect is caused by the destruction of a critical hydrogen bond to Ser113 in GP1. The lost hydrogen bond would lead to the subsequent loss of a large hydrogen-bonding network seen in the crystal structure \citep{Abraham2010}. In agreement with the static structure, our molecular dynamics simulations show Tyr211 to be involved in a large hydrogen-bonding network (results not shown).

@@

We also simulated several point mutations at Asn348 in the hTfR1. Asn348Lys is reported in the literature to cause reduced infectivity \textit{in vivo} \citep{Rad2008,Abraham2010}. Further, in the crystal structure two residues on GP1 and at least three on hTfR1, including Asn348, are involved in a fairly extensive hydrogen-bonding network. As discussed above, the alanine mutation at this site showed no significant difference in MAF or AUC from WT (Tables~\ref{tab:MAF_p} and ~\ref{tab:AUC_p}). In addition, the Asn348Lys mutation showed no significant difference from WT, and neither did Asn348Trp. (For both of these mutations, however, mean MAF and mean AUC was lower than for WT. See Table~\ref{tab:summary_statistics}.)  On the other hand, there was a detectable difference between Asn348Ala and Asn348Lys (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}), with Asn348Lys being a weaker binder. Moreover, Asn348Trp showed nearly identical results to Asn348Lys. These results suggest that, in contrast to Tyr211, the critical difference at position 348 in hTfR1 is size exclusion rather than the destruction of a hydrogen-bonding network. The mutations to large amino acids (Asn348Trp and Asn348Lys) produced nearly identical affinity changes, whereas the mutations to amino acids not capable of hydrogen bonding (Asn348Ala and Asn348Trp) produced significantly different affinity changes (Table~\ref{tab:pairwise_differences}). To check the consistency of our results, we hypothesized that the combination of Tyr211Ala and Asn348Trp, being chemically disconnected in two different hydrogen-bonding networks, would lead to a synergistic loss-of-binding. As expected, the double mutant was the weakest binding mutant tested ($ p < 10^{-6} $) (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}) in this study. Further, according to MAF (but not AUC), the combination of Tyr211Ala and Asn348Trp also showed significantly weaker binding than Tyr211Ala by itself (Tables~\ref{tab:MAF_p} and~\ref{tab:AUC_p}). We suspect that the effect of Asn348Trp alone is near the limit of detection using our method. A larger number of replicates would possibly have resolved affinity differences between Asn348Trp and WT or other mutants more consistently.

@@

By extending the SMD technique to investigate a protein--protein interaction we have, in many ways, changed the scope of its application. Traditionally this technique is either applied to compute equilibrium quantities via a non-equilibrium approximation \citep{Park2003,Park2004,Buch2011,Giorgino2012}, used to estimate protein stability through unfolding \citep{Lu1999}, or used to calculate the absolute free energy of small molecule ligand binding \citep{Dixit2001}. Likewise, others have used SMD to understand the process of binding and unbinding at a resolution unmatched by experiment \citep{Cuendet2011,Giorgino2012}. And still others aimed at more esoteric problems, such as applying driving forces to untie polypeptide knots in toy systems \citep{Sulkowska2010}. Here, we have shown that SMD can provide insight into the \textit{relative} strength of protein--protein interactions. In contrast to more traditional absolute affinity calculations, relative binding is much more useful for experimental application. Further, our method complements whole cell infectivity assays, which demonstrate phenotypic effects but do not provide biochemical mechanisms. Via SMD, one can separate mutations whose likely effect is altered binding affinity from mutations that may affect other factors such as protein expression, protein folding, or interactions with other proteins not considered in the simulation. Thus, SMD may open avenues for subsequent experimental work.

Our findings rationalize several effects observed in both infectivity data and rodent populations \citep{Rad2008,Rad20111}. We found that some substitutions at positions 211 and 348 did negatively affect the strength of viral binding. However, the computational data suggest that the reason and nature of the effects at these two sites are very different. Congruent with infectivity data \citep{Rad2008,Rad20111}, mutations at Tyr211 often have a dramatic effect on receptor binding. Tyr211Ala alone produces such a large decrease in affinity that it can be easily distinguished from the WT complex. Structural analysis reveals that the biochemical cause involves the destruction of a critical hydrogen-bonding network with Ser113 and vArg111 in GP1. Further, Tyr211Asp and Tyr211Thr were easily resolved from the WT complex, but they appear to cause an increase in affinity. As a result, we predict experimental structural analysis will show that Tyr211Asp and Tyr211Thr mutations cause a relatively dramatic tertiary structure deviation. Given that our model starts from an associated complex, it is not surprising that Tyr211Asp would cause increased rather than decreased affinity. Aspartate is charged rather than polar at physiological pH and its shorter side chain means the proteins would be pulled in closer apposition. Nevertheless, our results show Tyr211, or some other amino acid that is capable of hydrogen bonding, is necessary for a stable hydrogen-bonding network leading to efficient binding. Moreover, the cause of decreased infectivity seen in rodent populations with the Tyr211Asp mutation is not a simple change in binding affinity.

@@

Although our computational predictions largely agreed with the available literature, some mutations that are reported to cause reduced infectivity in experimental systems (most notably vArg111Ala and Asn348Lys, discussed above) were indistinguishable from the WT complex in our simulations. We would like to emphasize here that we cannot expect perfect agreement. While we have shown that our method can distinguish individual point mutations, we do not know the limit of detection with our method. First, it is possible that some mutants display measurable phenotypic effects in experiments yet appear identical under our method. More extensive sampling or refinement of the simulation protocol could help to differentiate such mutants (see also next paragraph). Second, the available experimental data for the GP1/hTfR1 system were generally obtained from infection assays, not binding assays. A mutant may cause a phenotypic difference in infectivity without generating a signal by our method. For example, infectivity could be lost in the experimental system because the protein is grossly or partially misfolded. An additional analytical step with circular dichroism or an analogous technique could clarify such large-scale folding differences. Further, since our simulations start with a bound structure, any changes that may dramatically affect the rate of association (different folds, trafficking issues, etc.) would be underestimated by our method. Finally, it is tempting to think only decreased binding affinity should correlate strongly with diminished infectivity. However, dramatically increased binding affinity could also disrupt infectivity by prohibiting cellular membrane detachment after viral invasion. The virus would be prevented from reaching its replication compartment (which is the cytosol in the case of Machupo) and could not reproduce.

@@

Making accurate predictions regarding the effects of non-alanine mutations at protein--protein interfaces remains  challenging. The main obstacle is the enormous number of chemically allowed three dimensional configurations in proteins \citep{Gumbart2012}. In theory, one could carry out all-atom simulations from physical first principles \citep{Gumbart2012} for very long time periods. After equilibrium is reached in such simulations, one could then compute a binding constant by observing the fractional association/dissociation time among two proteins. Unfortunately, due to limited computational power and available methods, reaching equilibrium with a simulated protein system is truly a herculean task and is essentially impossible at this time \citep{Gumbart2012}. There are two broadly useful computational approaches that avoid first-principles equilibrium simulations. First, to reduce computational complexity several studies have used rigid body docking and machine learning \citep{Vreven2011,Vreven2012,Bajaj2011,Hwang2010}. While these approaches can work well in certain scenarios, they often underperform in applications to novel systems, due to their dependence on available training data. Second, hybrid approaches exist that exploit non-equilibrium calculations within the context of all atom simulations \citep{Dixit2001,Is2001A,Is2001B,Park2004,Grant2011,Kortemme2004,Gumbart2012}. However, to date most of these methods have not been applied to protein--protein interactions, but rather to simpler scenarios such as protein--ligand interactions. What we have shown here is that hybrid non-equilibrium approaches can provide a useful and practical tool in studying protein--protein interactions.

@@

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/protein_comparison.pdf}}
\caption{\label{fig:protein_comparison}\title{The GP1/hTfR1 complex.} GP1 is shown in blue and hTfR1 is shown in green. (A) The full, de-glycosylated GP1/hTfR1 co-crystal structure. (B) The reduced structure used in SMD simulations.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/force_curve.pdf}}
\caption{\label{fig:force_curve}\title{Force versus distance curve of WT and the Y211A mutant.} The average force curve for 50 replicates of the WT complex is shown in black, and the average of 50 replicates of the Y211A mutant is shown in red. There is a large difference in both MAF and AUC between the two complexes.}
\end{figure}

\clearpage
\begin{figure}[p]
\centerline{\includegraphics[width=6in]{figures/sensitivity_histogram.pdf}}
\caption{\label{fig:sensitivity}\title{Distribution of interpolated maximum force (MAF) for three different GP1/hTfR1 complexes.} The WT GP1-hTfR1 complex in the middle is flanked by the tighter binding mutant Y211D on the right and the weaker binding double mutant N348W/Y211A on the left. The large non-overlapping areas indicate a large and statistically significant difference in these three complexes.}
\end{figure}
